Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-01-26 PAPER.tex
added text explaining how our data points are computed from the no-bootstrapping case

We smooth the 2D distribution of $P_{in}$ vs. $P_{out}$ using kernel density estimators. The result, for inverse covariance weighting, is shown in the left plot of Figure \ref{fig:sigloss_transfercurve}. Bayes' rule then simply instructs us to fix $\phat_{x}$ at our measured value, essentially reading Figure \ref{fig:sigloss_transfercurve} horizontally and reinterpreting Equation \eqref{eq:Bayes} as a function of $p(P_{in})$. The final result can then be normalized to give $p(P_{in} | \phat_{x})$. If $\phat_{x}$ itself does not take on a single value but is itself a distribution (for our analysis, this comes from bootstrapping), then one simply repeats the process for every single point on the distribution of $\phat_{x}$, before performing the final summation and normalization. In Figure \ref{fig:sigloss_transfercurve}, the peak of our data distribution $
\widehat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines. From the left plot (inverse covariance weighting), one can eyeball that a data value of $10^{5} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a 
value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim1000$. Performing a summation and normalization for the entire distribution of $\widehat{\textbf{p}}_{x}$ yields a final $P_{\rm in}$ distribution --- the distribution of our data as seen through the signal loss lens. We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals.

@@

We bootstrap PAPER-64 power spectra in order to determine confidence intervals for our results. In this section, we highlight 
one major changes in the way we estimate errors since A15, using the lesson we have learned about bootstrapping independent samples.

@@

>>>>

We smooth the 2D distribution of $P_{in}$ vs. $P_{out}$ using kernel density estimators. The result, for inverse covariance weighting, is shown in the left plot of Figure \ref{fig:sigloss_transfercurve}. Bayes' rule then simply instructs us to fix $\phat_{x}$ at our measured value, essentially reading Figure \ref{fig:sigloss_transfercurve} horizontally and reinterpreting Equation \eqref{eq:Bayes} as a function of $p(P_{in})$. The final result can then be normalized to give $p(P_{in} | \phat_{x})$. If $\phat_{x}$ itself does not take on a single value but is itself a distribution (for our analysis, this comes from bootstrapping, where our distribution is shifted so that its peak value aligns with the power spectrum estimate from the no-bootstrapping case; see Section \ref{sec:Boot} for more details on this), then one simply repeats the process for every single point on the distribution of $\phat_{x}$, before performing the final summation and normalization. In Figure \ref{fig:sigloss_transfercurve}, the peak of our data distribution $
\widehat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines. From the left plot (inverse covariance weighting), one can eyeball that a data value of $10^{5} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a 
value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim1000$. Performing a summation and normalization for the entire distribution of $\widehat{\textbf{p}}_{x}$ yields a final $P_{\rm in}$ distribution --- the distribution of our data as seen through the signal loss lens. We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals.

@@

We bootstrap PAPER-64 power spectra in order to determine confidence intervals for our results. In this section, we highlight 
one major change in the way we estimate errors since A15, using the lesson we have learned about bootstrapping independent samples.

@@

Finally, we note that our power spectrum points (previously computed as the mean of all bootstraps), is now computed as the power spectrum estimate resulting from not bootstrapping at all. More specifically, we compute one estimate without sampling over the baseline axis (all baselines are used), and this estimate is propagated through our signal loss computation along with the bootstrapped estimates (which are used to compute errors). The difference between taking the mean of the bootstrapped values and using the estimate from the no-bootstrapping case is small, but doing the latter ensures that we are forming results that reflect the maximum likelihood estimate of our data.
